\documentclass[12pt]{article}
\usepackage{pmmeta}
\pmcanonicalname{CharacterizationOfCompactlyGeneratedSpace}
\pmcreated{2013-03-22 19:10:04}
\pmmodified{2013-03-22 19:10:04}
\pmowner{karstenb}{16623}
\pmmodifier{karstenb}{16623}
\pmtitle{characterization of compactly generated space}
\pmrecord{4}{42074}
\pmprivacy{1}
\pmauthor{karstenb}{16623}
\pmtype{Theorem}
\pmcomment{trigger rebuild}
\pmclassification{msc}{54E99}
%\pmkeywords{quotient mapping}
%\pmkeywords{locally compact}
%\pmkeywords{final topology}
\pmdefines{C_k(X}
\pmdefines{Y)}

\endmetadata

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage[sort&compress]{natbib}

%\usepackage{psfrag}
%\usepackage{graphicx}
%%%\usepackage{xypic}

%theorems
\theoremstyle{definition}
\newtheorem{Def}{Definition}

\theoremstyle{plain}
\newtheorem{Lem}{Theorem}
\newtheorem{Lem2}{Lemma}
\newtheorem{Cor}{Corollary}
\newtheorem{Rem}{Remark}




\begin{document}
We give equivalent conditions when a Hausdorff topological space is compactly generated. First we need a definition.

\textbf{Definition.} Let $X$ be a $T_1$ space and $Y$ a topological space. We define $C_k(X, Y)$ to be the set of functions $f \colon X \to Y$ such that for every compact, closed set $K \subset X$ the restriction $f_{|K}$ is continuous. 

Clearly, $C(X, Y) \subset C_k(X, Y)$ for such spaces $X, Y$. With this we have the following theorem.

\textbf{Theorem.} Let $X$ be a Hausdorff space. Then the following conditions are equivalent.

\emph{i)} $X$ is compactly generated

\emph{ii)} $X$ carries the final topology generated by the family of inclusion mappings $(i_K \colon K \to X)_{K \subset X \ \text{compact}}$. 

\emph{iii)} For every topological space $Y$ we have $C_k(X, Y) = C(X, Y)$. 

\emph{iv)} $X$ is an image of a locally compact space under a quotient mapping.


\textbf{Remark.}
It follows easily from this that if there is a quotient mapping $f \colon X \to Y$ which maps a compactly generated space $X$ onto a Hausdorff space $Y$ then $Y$ is compactly generated.
%%%%%
%%%%%
\end{document}
